Job Demands-Resources model components through the lens of O*NET classifications

### 2022-12-03 Submission.Rmd
Updated Introduction

abstract: |
  O\*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource. All the results of this current study match the stress-appraisal stuff. Next steps: 1) discuss results within stress-appraisal framework (Lazarus & Bookman), 2) different literature on challenge and hindrance demands. Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings. JDR neglects the other 2 literatures. Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those. Maybe forget about cross-walk thing. May actually want to start with this: https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499.[^foot1]

@@

Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlight the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance. However, much of our existing knowledge of the way this model functions is grounded in the assumption that characteristics are generally considered resources or generally considered demands. We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (@webster2011extending) or that appraisals may change over time (CITE HERE). We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, which a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

@@

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job]. One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).

Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) [@bakker2014job]. Pertinent to the current study, demanding job characteristics are frequently often associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].

@@

As implied in the last paragraph, job context and characteristics are assigned or appraised as demands or resources. Although much of our research on job demands in particular is based on apriori classifications of demands [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand. The stress process speaks to how such individual difference in appraisal is possible. @lazarus1984stress presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis. Via this process, meaning is assigned to stimuli based on potential for gain or loss. If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping. The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress].

@@

The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (@cavanaugh2000empirical). @cavanaugh2000empirical delineated between two forms of demands – that of *challenge* and *hindrance* demands. Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement. Stressors like time pressure and responsibility are considered challenge stressors/demands. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes. This particular distinction between challenges and hindrances has been of value in determining what demands are related to various outcomes, whereby challenge stressors are typically associated with positive outcomes, and hindrance stressors, negative outcomes (e.g., @cavanaugh2000empirical).

However, one of the key questions we need to ask as researchers pertains to the very basic consideration of appraisals. In fact, this is one of several issues raised by @mazzola2019should in a recent review and meta-analysis of this framework. These authors cited the apriori assignment to stressors as a challenge or hindrance as a flawed assumption, suggesting that stressors are more likely to be a combination of both – challenge and hindrance appraisals. @lepine2022challenge, in a rebuttal to the @ mazzola2019should criticism, while acknowledging that the original challenge-hindrance stressor framework was based on the assertion that people tend to appraise specific work stressors ad challenges and other demands, noted that the appraisals likely served as a mediator.

We next consider the empirical evidence on this topic. The first obvious question is whether people perceive demands as challenges vs. hindrances, or whether all demands are under a larger “demands” category. Evidence suggests the employees do, in fact, distinguish between challenge and hindrance stressors [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending]. For example, @bakker2013weekly found that perceived work pressure as a hindrance demand, and emotional demands as more of a challenge demand. @webster2011extending approached this question with three common workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.

While their study did include resources, it nonetheless points to the possibility that demands might be differentially appraised and related to outcomes [e.g., @podsakoff2007differential]. The challenge-hindrance framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. For example, @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. In contrast, @abbas2019challenge found that challenge and hindrance stressors were *both* positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it [@crawford2010linking]. Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety [@rodell2009can]. Lastly, @gerich2017relevance concluded that employee well-being was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.

We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point. @podsakoff2007differential supported the original assertion of @cavanaugh2000empirical with regard to work outcomes such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover. The opposite pattern of relationship was observed for hindrance stressors. @kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals.

@@

@@

Add a description here of the exploratory stuff.

@@

>>>>

abstract: |
  O\*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource. All the results of this current study match the stress-appraisal stuff. Next steps: 1) discuss results within stress-appraisal framework [@lazarus1984stress], 2) different literature on challenge and hindrance demands. Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings. JDR neglects the other 2 literatures. Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those. Maybe forget about cross-walk thing. May actually want to start with this: https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499.[^foot1]

@@

Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlight the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance. However, much of our existing knowledge of the way this model functions is grounded in the assumption that characteristics are generally considered resources or generally considered demands. We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (@webster2011extending) or that appraisals may change over time (@rosen2020challenges). We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, which a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

@@

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job]. One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job). Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) [@bakker2014job]. Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience depsite the typical apriori assignment of a characteristic as objectively a "demand" or "resource". We explore this further below.

@@

As described in the last paragraph, job context and characteristics are assigned or appraised as demands or resources. Although much of our research on job demands in particular is based on apriori classifications of demands [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand. The stress process speaks to how such individual difference in appraisal is possible. @lazarus1984stress presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis. Via this process, meaning is assigned to stimuli based on potential for gain or loss. If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping. The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress]. Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor should an event or situation be deemed so. Although not suggested by the names, primary and secondary appraisals can happen simultaneously. For instance, available resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this ask).

@@

The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (@cavanaugh2000empirical). @cavanaugh2000empirical delineated between two forms of demands – that of *challenge* and *hindrance* demands. Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement. Stressors like time pressure and responsibility are considered challenge stressors/demands. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes. This distinction between challenges and hindrances has been of value in determining which demands are related to various outcomes. The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., @cavanaugh2000empirical).

Prior to considering the subsequent empirical work done on this topic, it is of value to explore *why* there is expected to be different outcomes associated with these forms of demands. @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes. Similar to the job-demands resources theory [@bakker2017job], challenge and hindrance demands elicit two different paths or processes. First, challenge stressors typically result in a challenge appraisal, and both engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. The other side of the coin is that this energy may be depleted eventually, leading to strain. Hindrance stressors elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].

We next consider the empirical evidence on this topic. The broadest, and perhaps first question, we should ask is whether people perceive demands as challenges vs. hindrances, or whether all demands are under a larger “demands” category. Evidence suggests the employees do, in fact, distinguish between challenge and hindrance stressors [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending]. For example, @bakker2013weekly found that perceived work pressure as a hindrance demand, and emotional demands as more of a challenge demand. @webster2011extending approached this question with three common workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees. @kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing. The opposite occurred when a demand was appraised as a hindrance – in those instances, the appraisal had a negative association with motivational resources.

Having evidence that people can make a distinction between challenge and hindrance stressors, the next logical question is whether they do relate differentially to outcomes. The challenge-hindrance stressor framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. For example, @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. @chen2021daily found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, @abbas2019challenge found that challenge and hindrance stressors were *both* positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it [@crawford2010linking]. Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety [@rodell2009can]. Lastly, @gerich2017relevance concluded that employee well-being was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.

We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes. For example, both challenges and hindrances have been shown to positively predict strain (@lepine2005meta; @podsakoff2007differential; @webster2010toward). Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction. For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressor [@lepine2005meta]. Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors [@podsakoff2007differential]. @kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals.

@horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model. In fact, @horan2020review state that “…stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p. 3). In fact, @horan2020review suggest future research continue to move away from apriori classifications of stressors, as doing so can be problematic for theoretical and empirical reasons. Theoretically, apriori classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., @searle2015merits). TRANSITION?

@@

##Current Study and Hypotheses

@@

Lastly, we propose three research that explicitly address a topic hinted at in the literature review above. Although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, there remains variability in these appraisals [@lepine2022challenge]. @lepine2022challenge, in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal. We explore whether literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job]and challenge-hindrance stressor framework [@cavanaugh2000empirical].

@@

So, what can be done about the findings that people experience both? @lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like train and support to offset the negative effects of challenging job demands.
